Estimating Correspondences of Deformable Objects ``In-the-wild"

### 2015-11-09 contents/evaluation.tex

>>>>

\paragraph{Results} We report the results in Figure \ref{fig:daam_benchmark} using Cumulative Error Distribution (CED) curves.

Through visual inspection we determined that fitting errors below 0.1 typically look plausible under the previous error measure where fitting errors below 0.6 for faces. Results show that, for this experiment, the fitting accuracy achieved by our dAAMs is marginally better to the one achieved by classic AAMs using intensity representations. In fact, classic AAM fail to improve the accuracy of the original initialisation on ears. Therefore the propose pipeline is capable of dealing with the complex structure of non-rigid shapes and learn dAAMs from simple curve line annotations that can compete and even surpass (in the case of a simple pixel intensity image representation) classic AAM, build from carefully annotated point landmarks, is quite remarkable.
